---
title: "Size vs. Movement"
output: html_notebook
---
```{r setup}
library(tidyverse)
library(geosphere)
library(lubridate)

source("~/db-connections.R")
leyte <- read_db("Leyte")

fish_db <- leyte %>% 
  tbl("clownfish") %>% 
  collect()


anem_db <- leyte %>% 
  tbl("anemones") %>% 
  collect() %>% 
  # we need dates for these anemones so I'm sticking the dive_db dates on here too
  left_join((leyte %>% tbl("diveinfo") %>% select(date, dive_table_id) %>% collect()), by = "dive_table_id")

# This data  was generated using the clownfish-demographics project
recap_w_lat <- read_csv("https://raw.githubusercontent.com/pinskylab/clownfish-demographics/master/data/recap_w_lat.csv?token=AG664YPECMP5WN5RW6EODDK5O67Y6", col_types = cols(.default = col_character())) %>% 
  mutate(fish_table_id = as.numeric(fish_table_id))

## Fish indiv 767 has a missing lat lon 
test <- recap_w_lat %>% 
  filter(fish_indiv == 767)

recap_w_lat <- recap_w_lat %>% 
  filter(fish_indiv != 767)
```

## Iterate through all of the capture events for fish and measure the distance between captures
```{r}
# create data holder
output <- tibble()

# create list of individuals - I'm using fish_table_id so that I measure each capture event against the others instead of just measuring the first against the others
fish <- recap_w_lat %>% 
  select(fish_table_id, fish_indiv) %>% 
  distinct()

for (i in seq(fish$fish_table_id)){
  current_fish <- recap_w_lat %>% 
    filter(fish_indiv == fish$fish_indiv[[i]])
  while(nrow(current_fish) > 1){
    cap_dist <- current_fish %>% 
      mutate(distance_m = distGeo(p1 = current_fish[1,c("lon", "lat")], p2 = current_fish[nrow(current_fish),c("lon", "lat")])) %>% 
      select(fish_table_id, fish_indiv, distance_m, date, site) %>% 
      distinct() 
    
    output <- rbind(output, cap_dist) %>% 
      distinct()
    
    current_fish <- current_fish %>% 
      slice(1:(nrow(current_fish)-1))
    }
}

```

## Attach fish meta data 
```{r}
fish_w_dist <- output %>% 
  left_join(select(fish_db, fish_table_id:recap), by = "fish_table_id")
```

## Attach anem meta data
```{r}
fish_w_anem <- fish_w_dist %>% 
  left_join(select(anem_db, anem_table_id:anem_obs), by = "anem_table_id")
```

## plot size vs. movement
```{r}
# keep only the oldest dates of capture
fish_w_dist_refined <- fish_w_dist %>% 
  select(fish_indiv, distance_m, size, date, sex) %>% 
  arrange(desc(date)) %>% 
  distinct(fish_indiv, distance_m, .keep_all = T) %>% 
  filter(!is.na(size))

ggplot(fish_w_dist_refined, aes(size, distance_m)) + 
  geom_point(aes(color = date)) +
  theme_classic()+
  theme(legend.position = "none") +
  labs(title = "Size vs. distance moved by clownfish in Leyte")

ggsave(here::here("plots", "size-movement-plot.png"))
```
## There does not appear to be a relationship between size and movement.

### If we remove the one fish that is an outlier, does the resolution reveal any relationship?
```{r}
remove_outlier <- fish_w_dist_refined %>% 
  filter(distance_m < 5000)

ggplot(remove_outlier, aes(size, distance_m)) + 
  geom_point(aes(color = date)) +
  theme_classic()+
  theme(legend.position = "none") +
  labs(title = "Size vs. distance (outlier removed)")

ggsave(here::here("plots", "size-movement-no-outlier-plot.png"))
```
## Is there a relationship between sex and movement?
```{r}
ggplot(filter(fish_w_dist_refined, !is.na(sex)), aes(sex, distance_m)) + 
  geom_point(aes(color = sex)) +
  theme_classic()+
  theme(legend.position = "none") +
  labs(title = "Sex vs. distance moved by clownfish in Leyte")

ggsave(here::here("plots", "sex-distance.png"))
```
```{r}
ggplot(filter(remove_outlier, !is.na(sex)), aes(sex, distance_m)) + 
  geom_point(aes(color = sex)) +
  theme_classic()+
  theme(legend.position = "none") +
  labs(title = "Sex vs. distance (outlier removed)", caption = "Both males and females move, but where they females in their prior capture?")
```

## Did they change sex between captures?
Make a list of fish that do not change sex between captures and replot
```{r}
same_sex <- fish_w_dist %>% 
  filter(!is.na(sex)) %>% 
  select(fish_indiv, sex) %>% 
  group_by(fish_indiv) %>% 
  distinct() %>% 
  filter(n() == 1)

ggplot(filter(remove_outlier, fish_indiv %in% same_sex$fish_indiv, !is.na(sex)), aes(sex, distance_m)) + 
  geom_point(aes(color = sex)) +
  theme_classic()+
  theme(legend.position = "none") +
  labs(title = "Sex vs. distance (same sex between captures)", caption = "Both males and females move")

ggsave(here::here("plots", "no-sex-change-distance.png"))
```

## Did we see the anemone of the previous capture year?
```{r}
# Make a list of fish_indivs that have anem info
fish_list <- fish_w_anem %>% 
  filter(!is.na(anem_id) | !is.na(anem_obs)) %>% 
  select(fish_indiv) %>% 
  distinct() 

output <- tibble(fish_indiv = NA, date = NA, anem_id = NA, old_anem_id = NA, anem_obs = NA, second_year = NA, later_year = NA)

for(i in seq(fish_list$fish_indiv)){
  # on which anemones was this fish observed?
  recap_fish <- fish_w_anem %>% 
    filter(fish_indiv == fish_list$fish_indiv[i]) %>% 
    select(fish_indiv, date, anem_id, old_anem_id, anem_obs) %>% 
    distinct() %>% 
    arrange(date) %>% 
    filter(!is.na(anem_id) | !is.na(anem_obs)) %>% 
    mutate(second_year = NA, later_year = NA)
  
  
  # if the anemones were different, did we see the first anemone again in the second capture year?
  if(nrow(distinct(recap_fish, anem_obs)) == nrow(recap_fish)){
    # get the year of the second capture event
    year_second_capture <- recap_fish %>% 
      slice(2) %>% 
      mutate(year = lubridate::year(date)) %>% 
      select(year)
    
    # get the observation id of the first anemone
    first_anem <- recap_fish %>% 
      slice(1) %>% 
      select(anem_obs)
    
    # check the database to see if the first anemone was observed in the second year
    observed <- anem_db %>% 
      filter(anem_obs == first_anem$anem_obs) %>% 
      mutate(year = year(date)) %>% 
      filter(year == year_of_second_capture$year)
    if(nrow(observed) == 0){
      recap_fish <- recap_fish %>% 
        mutate(second_year = F)
      # check to see if the first anemone was observed ever again after the second capture
      observed <- anem_db %>% 
      filter(anem_obs == first_anem$anem_obs) %>% 
      mutate(year = year(date)) %>% 
      filter(year > year_of_second_capture$year)
      if(nrow(observed) == 0){
        recap_fish <- recap_fish %>% 
        mutate(later_year = F)
      }else{
        recap_fish <- recap_fish %>% 
        mutate(later_year = T)
      }
    
    }else{
      recap_fish <- recap_fish %>% 
        mutate(second_year = T)
    }
    
  }
  output <- rbind(output, recap_fish)
  

}

```

